---
title: "Leaflet Interactive Map"
author: "Pratyusa Mukherjee"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

## `r format(Sys.Date(), "%B %d, %Y")`

## Map of Ivy League Universities and Associated Cost

#### The following is a simple map, built using leaflet, displaying the locations of all of the colleges/universities in the Ivy League. Clicking on each icon on the map will display the name of the college/university (which links to the school's home page), as well as the overall annual cost of attending the school as an undergraduate.

```{r}
suppressMessages(library(leaflet))

ivyicon <- makeIcon(
  iconUrl ="ivl.jpg", iconWidth=45*215/230, iconHeight = 35, 
  iconAnchorX = 35*215/230/2, iconAnchorY = 26)
ivySites <- c(
"<a href='http://www.harvard.edu/'>Harvard University</a><BR> Cost: $67K",
"<a href='http://www.yale.edu'>Yale University</a><BR> Cost: $68K",
"<a href='http://www.brown.edu/'>Brown University</a><BR> Cost: $65K",
"<a href='http://www.cornell.edu/'>Cornell University</a><BR> Cost: $68K",
"<a href='http://www.columbia.edu/'>Columbia University</a><BR> Cost: $72K",
"<a href='http://www.dartmouth.edu/'>Dartmouth College</a><BR> Cost: $67K",
"<a href='http://www.princeton.edu/'>Princeton University</a><BR> Cost: $64K",
"<a href='http://www.upenn.edu/'>University of Pennsylvania</a><BR> Cost: $69K"
)
lativy <- c(42.3770, 41.3163, 41.8268, 42.4534, 40.8075, 43.7044, 40.3573,39.9522)
lonivy <- c(-71.1167, -72.9223, -71.4025, -76.4735, -73.9626, -72.2887, -74.6672, -75.1932
)

ivydf <- data.frame(latitude = lativy, longitude = lonivy)
ivydf %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = ivyicon, popup = ivySites)
``` 
